\documentclass[11pt]{article}

% Exact Float Counter CRDTs — arXiv preprint (cs.DC).
% Build: pdflatex exact-float-crdts.tex  (twice, for refs).

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{enumitem}

\hypersetup{colorlinks=true,linkcolor=black,citecolor=black,urlcolor=blue}

% Let TeX absorb slack in code-heavy paragraphs (\texttt tokens don't hyphenate)
% rather than pushing lines into the margin.
\emergencystretch=3em

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{proposition}[theorem]{Proposition}

\lstset{basicstyle=\ttfamily\small,columns=fullflexible,breaklines=true,frame=single,
        keywordstyle=\color{black}\bfseries,commentstyle=\color{gray}}

\title{Exact Float Counter CRDTs:\\
Lawful, Machine-Checked Convergence for Replicated Floating-Point Sums}

\author{Kyle Clouthier\\
\small Clouthier Simulation Labs \\
\small \texttt{kyle@simgen.dev} \quad \url{https://simgen.dev}}

\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Counter CRDTs (Conflict-free Replicated Data Types) have been \emph{integer-valued} for fifteen years.
The reason is algebraic: a state-based counter's merge must be commutative, associative, and idempotent,
and IEEE-754 floating-point addition is neither commutative nor associative \emph{in the accumulated
state}---so a floating-point sum cannot lawfully instantiate the standard construction, and its replicas
do not converge to identical values. We observe that an \emph{exact, mergeable superaccumulator}---a
fixed-point integer wide enough to hold every finite \texttt{f64} exactly---restores precisely the
missing properties, making the standard state-based counter-CRDT construction lawful for floating-point
sums. We give the construction, machine-check its convergence laws in Lean~4 (the merge is a
join-semilattice; folding \emph{any} delivery schedule---arbitrary reordering and duplication---yields the
same state; merges are monotone; and the converged read equals the exactly rounded sum of every
increment), and provide a canonical byte encoding so replicas prove convergence by comparing a hash
rather than an $\varepsilon$. We are deliberate about novelty. The superaccumulator is
classical~\cite{kulisch,neal,demmel}; the counter-CRDT template is standard~\cite{shapiro}; the
contribution is the \emph{lawful instantiation for exact floating-point}, the mechanized convergence
laws, and a torture-tested open-source implementation. We situate the result against mechanized-CRDT
work~\cite{gomes}, which verifies an \emph{integer} counter within a network model; our added dimension
is exactness for continuous values, not a new verification framework. Code, proofs, and a reproducible
torture test are public.
\end{abstract}

\section{Introduction}

A replicated counter that any node can increment, that tolerates arbitrary message reordering,
duplication, and partition, and that converges without coordination, is one of the foundational
Conflict-free Replicated Data Types~\cite{shapiro}. The grow-only counter (G-Counter) and its
signed cousin (PN-Counter) are textbook. Every widely deployed implementation we are aware of counts
\emph{integers}: Redis Enterprise Active-Active documents 59-bit integer counters~\cite{redisdocs};
Akka's \texttt{GCounter} is \texttt{BigInt}-valued; Riak's counters are integers.

This is not an oversight. A state-based CRDT converges because its merge $\sqcup$ forms a
\emph{join-semilattice}: commutative, associative, and idempotent~\cite{shapiro}. A G-Counter meets
this by storing one non-negative integer per replica and merging entrywise with $\max$, which inherits
those properties from the integers. If one tries to replace the per-replica integer with a
floating-point running sum, the construction breaks at the algebra: IEEE-754 addition is
non-associative---$(a \oplus b) \oplus c \ne a \oplus (b \oplus c)$ in general---so two replicas that
receive the same increments in different orders hold different bit patterns, and merging those states is
neither well-defined nor convergent. A recent generic counter library makes the requirement explicit by
being parametric over a commutative semigroup; \texttt{f64} under $\oplus$ is simply not a lawful
argument. The result is a fifteen-year gap: no lawful floating-point counter CRDT.

The gap is worth closing because floating-point aggregates that must converge are common: replicated
metrics, offline-first sums that reconcile on sync, multi-region billing totals that different replicas
compute in different orders. The usual workaround is to ban floats from replicated state
entirely---the deterministic-simulation-testing discipline does exactly this---or to accept
``eventually approximately equal'' and reconcile with a tolerance, which forfeits the CRDT's exact,
hash-checkable convergence.

\paragraph{Contribution.} We make one observation and follow it through with proofs and code.
\begin{enumerate}[leftmargin=1.4em,itemsep=1pt]
  \item \textbf{Observation.} An \emph{exact, mergeable} accumulator---a wide fixed-point integer
  (a \emph{superaccumulator}) that represents every finite \texttt{f64} exactly---makes floating-point
  summation associative and commutative \emph{in the accumulated state, by construction}, because
  integer addition is. This restores exactly the algebra the counter-CRDT construction requires.
  \item \textbf{Construction.} The standard state-based counter recipe, instantiated with this
  accumulator, yields a G-Counter whose value is an \emph{exactly rounded} floating-point sum
  (\S\ref{sec:construction}).
  \item \textbf{Mechanized convergence.} We model the construction in Lean~4 and machine-check its
  convergence laws: the merge is a join-semilattice; folding any delivery schedule (any permutation,
  any duplicates) yields the same state; merges are monotone; and the converged full-knowledge read
  equals the exact sum of every increment (\S\ref{sec:proofs}). The proofs carry no \texttt{sorry} and
  use only Lean's standard axiom base.
  \item \textbf{Hash-checkable convergence.} The accumulator has a canonical byte encoding, so converged
  replicas prove agreement by comparing a hash rather than an $\varepsilon$ (\S\ref{sec:encoding}).
  \item \textbf{Implementation.} An open-source Rust implementation, torture-tested across randomized
  gossip schedules with duplicate and stale delivery, converges byte-identically where a naive
  \texttt{f64} counter does not (\S\ref{sec:eval}).
\end{enumerate}

\paragraph{What this is not.} We claim no new algorithm and no new verification framework. The
superaccumulator is classical~\cite{kulisch,neal,demmel}; the counter-CRDT template is
standard~\cite{shapiro}; machine-checked CRDTs exist~\cite{gomes}. The novelty is the composition---a
\emph{lawful, exact} floating-point counter CRDT with mechanized convergence laws and a canonical
encoding---and the honest engineering that makes it checkable. We state prior art up front
(\S\ref{sec:related}) and invite correction: if an exact floating-point counter CRDT with mechanized
laws already exists, we have not found it.

\section{Background}

\paragraph{State-based CRDTs.} A state-based (convergent) CRDT is a join-semilattice
$(S, \sqcup)$: replicas hold states in $S$, update locally by moving up the lattice, and merge with
$\sqcup$, which must be commutative, associative, and idempotent. Strong eventual consistency follows:
replicas that have observed the same set of updates hold equal state, regardless of message order,
duplication, or delay~\cite{shapiro}.

\paragraph{The G-Counter.} A grow-only counter over replicas $\{0,\dots,R-1\}$ is a map
$g : \mathrm{Fin}\,R \to \mathbb{N}$. Replica $r$ increments by raising its own entry $g(r)$;
$(g \sqcup h)(r) = \max(g(r), h(r))$; the value is $\sum_r g(r)$. Commutativity, associativity, and
idempotence of $\sqcup$ are inherited from $\max$ on $\mathbb{N}$. Only the owner writes its entry, so
concurrent increments never conflict.

\paragraph{Why floats break it.} Replace $g(r) \in \mathbb{N}$ with a floating-point running sum
$s(r) \in \texttt{f64}$ accumulated from replica $r$'s increment stream. Because $\oplus$ is
non-associative, $s(r)$ depends on the \emph{order} in which $r$ applied its increments, and two
replicas relaying $r$'s increments in different orders disagree on $s(r)$ bit-for-bit. ``Highest count
wins'' has nothing to select on, and merging by re-adding floats compounds the non-associativity.
The read $\sum_r s(r)$ is itself order-dependent. Convergence to identical values fails.

\paragraph{Exact superaccumulators.} An exact summation accumulator represents the running sum as a
wide fixed-point integer rather than a float. Every finite \texttt{f64} is an integer multiple of
$2^{-1074}$; a two's-complement integer of a few thousand bits holds any such value, and any sum of a
bounded number of them, \emph{exactly}. Integer addition into this accumulator is associative and
commutative, so the accumulated state is independent of summation order by construction; a single
correctly-rounded conversion at read time recovers an \texttt{f64}. The idea is classical: Kulisch's
exact dot-product accumulator~\cite{kulisch}, Neal's superaccumulators~\cite{neal}, and the
Demmel--Nguyen reproducible-summation line~\cite{demmel}. Our implementation uses a 2176-bit
two's-complement accumulator in units of $2^{-1074}$; the details of the accumulator are not the
contribution and we treat it as a black box with one property, stated next.

\begin{definition}[Exact mergeable accumulator]\label{def:acc}
An \emph{exact mergeable accumulator} is a type $A$ with an injection $\iota : \texttt{f64}_{\mathrm{fin}}
\to \mathbb{Z}$ (the exact value in units of $2^{-1074}$), an empty state $\bot_A$ with model value $0$,
an operation $\mathsf{add} : A \times \texttt{f64}_{\mathrm{fin}} \to A$ whose model is $s \mapsto s +
\iota(x)$, and a merge $\mathsf{merge} : A \times A \to A$ whose model is integer addition. It exposes a
monotone $\mathsf{count} : A \to \mathbb{N}$ (the number of $\mathsf{add}$s) and a canonical encoding
$\mathsf{bytes} : A \to \{0,1\}^{*}$ with $\mathsf{bytes}(a) = \mathsf{bytes}(b) \iff a = b$.
\end{definition}

Because the accumulator's state is an integer under addition, $\mathsf{merge}$ is exactly commutative
and associative---the two properties floating-point addition lacks and the counter-CRDT construction
requires.

\section{The Exact Float Counter CRDT}\label{sec:construction}

We instantiate the standard state-based G-Counter with the exact accumulator of
Definition~\ref{def:acc}.

\paragraph{State.} A replica holds a map from replica id to an exact accumulator,
$\mathsf{GC} : \mathrm{Fin}\,R \to A$, with entry $r$ owned by replica $r$.

\paragraph{Increment.} To add a floating-point value $x$, replica $r$ applies $\mathsf{add}(-, x)$ to
its own entry. Entries are append-only: a replica only ever adds to its own accumulator, so its
sequence of own-states is totally ordered by $\mathsf{count}$.

\paragraph{Merge.} The join is entrywise ``highest count wins'':
\[
(s \sqcup t)(r) \;=\;
\begin{cases}
s(r) & \text{if } \mathsf{count}(s(r)) \ge \mathsf{count}(t(r)),\\
t(r) & \text{otherwise.}
\end{cases}
\]
Because entry $r$ is append-only and owned by $r$, the entry with the larger count strictly contains the
smaller one's increments; equal counts imply equal state. This is the standard counter-CRDT join, and it
is where exactness matters: two relayed copies of replica $r$'s accumulator at the same count are
\emph{byte-identical} precisely because the accumulator is order-invariant---the property a float sum
lacks.

\paragraph{Read.} The counter's value is $\mathsf{value}\!\left(\bigsqcup_r \mathsf{merge\text{-}all}\right)$:
merge every entry's accumulator and convert once, with a single correct rounding. Merge order is
irrelevant by the accumulator's associativity/commutativity.

\paragraph{Idempotence and deduplication.} As with every counter CRDT, the \emph{entry-level} join is
idempotent (re-merging an entry at the same count is a no-op), but merging an accumulator's raw state
into itself would double-count; deduplication is the map layer's responsibility, exactly as in the
integer case~\cite{shapiro}. What the exact accumulator supplies is the missing piece for floats: a
deterministic, exact, commutative-associative entry state with a canonical encoding.

\section{Machine-Checked Convergence}\label{sec:proofs}

We model the construction in Lean~4 (core only, no \texttt{mathlib}) and prove its convergence laws.
The model reflects the append-only invariant: because entry $r$ is append-only and owned by $r$, an
entry is faithfully represented by \emph{how many} increments it contains, so ``highest count wins'' on
same-replica entries is $\max$ on those counts (equal counts imply equal state, by construction). A
counter state is one count per replica, $\mathsf{GC}\,R = \mathrm{Fin}\,R \to \mathbb{N}$, and the join
is the pointwise $\max$. The exact-value facts (that folding increments in any order gives the same
integer state, and that the read is the exactly rounded sum) are inherited from a separate, independently
machine-checked order-invariance result for the accumulator itself.

\begin{theorem}[Join semilattice]\label{thm:lattice}
The join is commutative, associative, and idempotent:
$s \sqcup t = t \sqcup s$, $(s\sqcup t)\sqcup u = s\sqcup(t\sqcup u)$, and $s \sqcup s = s$.
\end{theorem}

\begin{theorem}[Delivery-schedule invariance]\label{thm:sched}
Let $\mathsf{joinAll}$ fold a list of received snapshots into a replica's state. For any two lists
related by a permutation, $\mathsf{joinAll}$ yields the same state; and receiving the same snapshot
twice in succession changes nothing. Consequently \emph{any} delivery schedule---arbitrary reordering
and arbitrary duplicate deliveries---produces the same state.
\end{theorem}

\begin{theorem}[Monotonicity]\label{thm:mono}
For all $s,t$ and $r$, $s(r) \le (s \sqcup t)(r)$: a merge never discards an increment either side knows.
\end{theorem}

\begin{theorem}[Exact read]\label{thm:read}
The full-knowledge state---every increment of every replica---reads the exact sum of every increment.
Combined with the accumulator's order-invariance, this is byte-for-byte the state any ordering or
sharding of those same increments produces.
\end{theorem}

The Lean development discharges Theorems~\ref{thm:lattice}--\ref{thm:read} (as
\texttt{join\_comm}, \texttt{join\_assoc}, \texttt{join\_idem}, \texttt{joinAll\_perm\_invariant},
\texttt{joinAll\_dup\_invariant}, \texttt{le\_join\_left}, and \texttt{read\_full\_exact}), plus an
absorption lemma showing the full-knowledge state is the top of the reachable lattice. A CI job audits
every theorem's axiom dependencies: all reduce to Lean's standard base (\texttt{propext},
\texttt{Classical.choice}, \texttt{Quot.sound}); none uses \texttt{sorryAx}. The order-invariance of the
accumulator (that folding increments in any order, or by any merge tree, gives the same integer state)
and the correctness of the final rounding are proved in a companion development and additionally checked
at the bit level by bounded model checking of the Rust implementation.

\paragraph{Honest scope of the proofs.} The Lean proofs establish the value-level algebra of the
construction. That the Rust map layer increments \texttt{count} per \texttt{add} and applies
``highest-count-wins'' per entry is a small trusted surface, exercised (not proved) by the randomized
torture test of \S\ref{sec:eval}. Deduplication semantics are the map layer's, as in every counter CRDT.
We claim mechanized \emph{convergence laws for the construction}, not end-to-end verification of a
production system.

\section{Canonical Encoding and Hash-Checkable Convergence}\label{sec:encoding}

The exact accumulator serializes to a fixed-size canonical byte string with
$\mathsf{bytes}(a)=\mathsf{bytes}(b)\iff a=b$ (Definition~\ref{def:acc}). A counter state therefore has
a canonical encoding (the concatenation of its entries' encodings under a fixed replica order), and two
replicas that have converged hold byte-identical state. This upgrades convergence testing from an
approximate, threshold-based comparison to an exact one: replicas prove agreement by exchanging and
comparing a hash of the canonical bytes, and any disagreement is a single-bit event rather than an
$\varepsilon$ judgment call. For float aggregates this is qualitatively new---an ordinary float sum has
no canonical state to hash---and it is what makes the CRDT's convergence \emph{auditable} rather than
merely asymptotic.

\section{Implementation and Evaluation}\label{sec:eval}

We implement the construction in Rust over an exact 2176-bit superaccumulator with a 289-byte canonical
encoding. The construction is exercised by a randomized adversarial harness intended to break it:

\begin{itemize}[leftmargin=1.4em,itemsep=1pt]
  \item eight replicas, each adding its own stream of hostile values (mixed magnitudes across many
  decades, subnormals, and exact-cancellation pairs);
  \item 300 randomized gossip schedules, each interleaving local increments with snapshot exchanges that
  include \emph{duplicate delivery} and \emph{stale snapshots}, followed by a partition-heal
  anti-entropy sweep;
  \item after quiescence, every replica's canonical state and every converged value are compared.
\end{itemize}

Across all 300 schedules every replica converged \emph{byte-identically}, and every converged value
equalled the exactly rounded sum of all increments. As a contrast, re-summing the \emph{same} converged
per-replica values in forward versus reverse order with naive \texttt{f64} addition produced different
bit patterns in 184 of 300 schedules---evidence that exactness is load-bearing here, not decorative. The
same code compiles to WebAssembly and reproduces the identical canonical hash as native x86-64 and
ARM64, so cross-architecture replicas agree bit-for-bit.

We report cost honestly. Exact accumulation is roughly $5$--$10\times$ a naive summation loop and
$1.2$--$2.5\times$ compensated (Kahan) summation on mixed-magnitude data; merging shard states is
effectively free (hundreds of nanoseconds per merge). This is the price of an exact, mergeable,
canonically-encoded state, and it is paid where bit-identity matters---replicated aggregates,
signed/hashed outputs, cross-machine reconciliation---not in a hot inner loop.

\section{Related Work}\label{sec:related}

\paragraph{CRDTs and counters.} Convergent and commutative replicated data types, and the
join-semilattice characterization of state-based convergence, are due to Shapiro et
al.~\cite{shapiro}. Counter CRDTs in that framework, and in every deployment we know of, are
integer-valued: Redis Enterprise Active-Active documents 59-bit integer counters~\cite{redisdocs};
Akka and Riak counters are integers. Generic counter libraries are parametric over a commutative
semigroup, which \texttt{f64} under $\oplus$ does not lawfully inhabit---the precise gap this note
closes.

\paragraph{Mechanized CRDTs.} Gomes, Kleppmann, Mulligan, and Beresford give an
Isabelle/HOL framework with an explicit network model and machine-checked strong eventual consistency
for an increment/decrement counter, an Observed-Remove set, and a Replicated Growable
Array~\cite{gomes}. Their framework is more thorough on the distributed-systems side than our
development---it models the network and proves consistency over all network behaviours---and their
counter is the \emph{integer} case. Our contribution is orthogonal: exactness for a
\emph{floating-point} aggregate, via a lawful accumulator, with the convergence laws mechanized. We do
not contribute a verification framework and we do not model the network; combining an exact-accumulator
counter with a network-model framework such as theirs is natural future work.

\paragraph{Exact and reproducible summation.} The exact accumulator we rely on is classical:
Kulisch's exact accumulator~\cite{kulisch}, Neal's superaccumulators~\cite{neal}, and the
Demmel--Nguyen / ReproBLAS reproducible-summation line~\cite{demmel}. These make summation
order-independent on one machine; we use one such accumulator as the lawful monoid a counter CRDT needs.
Reproducible aggregation has also been studied in databases~\cite{muller}, single-node and without a
mergeable or serializable accumulator state.

\paragraph{The honest question.} The individual ingredients are known. We searched for an exact
floating-point counter CRDT with mechanized convergence laws and did not find one; if it exists, we
would like to cite it and correct this note.

\section{Beyond counters: convergent statistics}
\label{sec:stats}

The construction generalizes past counters. Any statistic whose sufficient state is a set of
\emph{exact monomial sums} ($\sum x_i$, $\sum x_i^2$, $\sum x_i^3$, $\sum x_i^4$, $\sum x_i y_i$, \dots)
inherits the whole contract: each sum lives in its own exact accumulator, so the composite state is a
product of lawful monoids and the merge laws lift componentwise (and pointwise for keyed families);
these lifting laws are machine-checked in \texttt{proofs/ToolkitAlgebra.lean}. Reads are computed from
the exact integer state in big-integer arithmetic with a \emph{single} final round-to-nearest-even, so
every read that is a rational function of the state is the \emph{correctly rounded value of the true
statistic}: mean, population and sample variance, covariance, least-squares slope and intercept, and
$R^2$. Two cases are worth noting: Pearson kurtosis $\mu_4/\mu_2^2$ and squared skewness
$\mu_3^2/\mu_2^3$ are exactly rounded because the sample-size and unit factors cancel, leaving a pure
rational of the state; reads involving a square root (standard deviation, correlation, skewness) apply
one IEEE-correctly-rounded \textsf{sqrt} to an exactly rounded radicand---at most two roundings, still
bit-identical everywhere. Exact retraction (a positive/negative pair of moment states) gives
insert-then-delete reads that return to byte-identical values, and exact covariance \emph{matrices}
support multiple linear regression whose normal-equation entries are exactly rounded (the solve itself
is a fixed deterministic elimination: bit-invariant, not exactly rounded---a stated second tier).

The classical mergeable-moments art makes the contrast precise. The pairwise update formulas of Chan,
Golub, and LeVeque~\cite{chan} are \emph{algebraically} exact but computed in floating point: the
resulting bits depend on the merge tree, and the merge double-counts on re-delivery. Mergeable
summaries~\cite{agarwal} are mergeable by design but approximate. Reproducible reductions in the
ReproBLAS lineage achieve bit-identity by \emph{pinning} an operation order. Exact,
order-invariant-without-pinning, and CRDT-lawful appears to be an unoccupied combination; as with the
counter itself, we state this as a question rather than a claim of priority. The generalization
ships in the implementation's \texttt{stats} feature (v0.2), with each read verified against an
independent big-integer oracle by a neighbor-comparison correct-rounding check, including
catastrophic-cancellation regimes (mean $10^8$, spread $10^{-3}$: the textbook one-pass formula returns
a \emph{negative} variance; the reads here are exactly rounded). The two-product domain limits apply per
monomial and are detected, never silent.

\section{Limitations}

The Lean proofs establish the construction's value-level algebra, not an end-to-end verification of the
implementation; the map layer's per-entry count and dedup are trusted and tested rather than proved
(\S\ref{sec:proofs}). Like every counter CRDT, deduplication of repeated shards is the map layer's job;
$\mathsf{merge}$ alone is not idempotent. The accumulator's cost (\S\ref{sec:eval}) makes this suitable
for aggregates where bit-identity is the point, not for high-throughput inner loops. Finally, the
statistics of \S\ref{sec:stats} inherit these limits per monomial sum (narrowing the certified input
domain for third and fourth moments), and order statistics (medians, quantiles) admit no exact mergeable
state at all---fixed-bucket histograms with exact counts and honest quantile \emph{bounds} are the
boundary of the family.

\section{Conclusion}

Counter CRDTs were integer-only because their merge must be commutative and associative and floating-point
addition, in the accumulated state, is neither. An exact, mergeable superaccumulator restores exactly
those properties, making the standard construction lawful for floating-point sums. The result is a
floating-point counter CRDT whose convergence laws are machine-checked, whose converged value is an
exactly rounded sum, and whose agreement is provable by a hash rather than an $\varepsilon$. The
primitives are old and cited; the contribution is the lawful composition, the mechanized laws, and a
public, torture-tested implementation. We hope the honest framing---prior art first, a named question
about missing work, and calibrated claims---is itself useful in a subfield where the interesting move
is often a lawful instantiation rather than a new algorithm.

\paragraph{Artifacts.} The implementation, the Lean proofs (with the axiom-audit CI job), and the
randomized torture test are available as open source (MIT/Apache-2.0) at
\url{https://github.com/KyleClouthier/bitrep}; the exact float counter CRDT is the
\texttt{float\_gcounter} example, the convergence proofs are \texttt{proofs/FloatGCounter.lean}, and
the convergent statistics of \S\ref{sec:stats} are the \texttt{stats} feature (v0.2 on crates.io) with
merge-algebra proofs in \texttt{proofs/ToolkitAlgebra.lean}. A browser demonstration of the underlying
exact accumulator is at \url{https://simgen.dev/bitrep/}.

\begin{thebibliography}{9}
\bibitem{chan} T.~F.~Chan, G.~H.~Golub, and R.~J.~LeVeque.
  \emph{Algorithms for Computing the Sample Variance: Analysis and Recommendations.}
  The American Statistician 37(3), 1983.
\bibitem{agarwal} P.~K.~Agarwal, G.~Cormode, Z.~Huang, J.~M.~Phillips, Z.~Wei, and K.~Yi.
  \emph{Mergeable Summaries.} PODS 2012.
\bibitem{shapiro} M.~Shapiro, N.~Pregui\c{c}a, C.~Baquero, and M.~Zawirski.
  \emph{Conflict-free Replicated Data Types.} SSS 2011.
\bibitem{gomes} V.~B.~F.~Gomes, M.~Kleppmann, D.~P.~Mulligan, and A.~R.~Beresford.
  \emph{Verifying Strong Eventual Consistency in Distributed Systems.} OOPSLA 2017 / PACMPL 1(OOPSLA).
\bibitem{kulisch} U.~Kulisch. \emph{Computer Arithmetic and Validity: Theory, Implementation, and
  Applications.} de Gruyter, 2008.
\bibitem{neal} R.~M.~Neal. \emph{Fast Exact Summation Using Small and Large Superaccumulators.}
  arXiv:1505.05571, 2015.
\bibitem{demmel} J.~Demmel and H.~D.~Nguyen. \emph{Fast Reproducible Floating-Point Summation.}
  IEEE ARITH 2013; see also ReproBLAS.
\bibitem{muller} I.~M\"uller, A.~Arteaga, T.~Hoefler, and G.~Alonso.
  \emph{Reproducible Floating-Point Aggregation in RDBMSs.} ICDE 2018.
\bibitem{redisdocs} Redis. \emph{Active-Active database strings and counters (59-bit integer counters).}
  Redis Enterprise documentation.
\end{thebibliography}

\end{document}
